---
title: "Homework 3"
author: "Ama Konadu Appau"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
```


Question 1

1)  For the vector given above, use and show two methods of R coding to extract the first 
element and the last element.
```{r}
Vector1 <- (c( 10, 19, 121, 83, 63, 7, 77, 61, 51, 97, 123, 41))
Vector1[c(1,12)]
Vector1[-c(2,3,4,5,6,7,8,9,10,11)]
```

Question 2
For the vector given above, use and show two methods of R coding to extract all of the 
elements that are less than 60
```{r}
Vector1[Vector1>60]
for (i in Vector1) {
  if (i>60)
  print(i)
}
```
Question 3
For the vector given above, use and show two methods of R coding to extract all numbers
that are not divisible by 2 or 3.
```{r}
Vector1[!Vector1%%2==0 & !Vector1%%3==0 ]
for (i in Vector1) {
  if (i%%2!=0 & i%%3!=0 )
    print(i)
}
```
Question 4
```{r}
is.na(Vector1)
Vector1[Vector1=="NA"]
```
Question 5
 For the list given above, use and show R coding to confirm that “pear” is a character 
element.
```{r}
myList <-  list(TRUE, 12.35, "pear", 48, c = 3:8, list(23, "team"))
myList <-  list(TRUE, 12.35, g = "pear", 48, c = 3:8, list(23, "team"))
typeof(myList$g)
```
Question 6
For the list given above, use and show R coding to extract the first three elements of the list.
```{r}
myList[c(1:3)]
```
Question 7
Use the $ operator to extract the element “pear” from your list. Be sure to use and show 
required R code to produce the requested output
```{r}
myList <-  list(TRUE, 12.35, g = "pear", 48, c = 3:8, list(23, "team"))
myList$g
```

Question 8
 Use and show R code to write a function to solve the following quadratic equations by using 
the quadratic formula.  (all equations have two real number solutions)
a)  x2- 3x - 28 = 0                                                                                                                                              
b)  x2 + x  - 30 = 0                                                                                                                                           
c) 3x2+ 14x + 8 = 0                                                                                                                                        
d) 2x2+11x = 6
```{r}

qf<-function(a,b,c)
{
  X1=(-1*b +(b**2-(4*a*c))**1/2)/(2*a)
  X2=(-1*b -(b**2-(4*a*c))**1/2)/(2*a)
  return(c(X1,X2))
  }
qf(1,-3,-28)
```
Question 9

```{r}
tb <- tibble::tibble(x = 1:5, y = 5:1)
typeof(tb)
#> [1] "list"
attributes(tb)
#> $class
#> [1] "tbl_df"     "tbl"        "data.frame"
#> 
#> $row.names
#> [1] 1 2 3 4 5
#> 
#> $names
#> [1] "x" "y"
```


Question 10
```{r}
 %>%
  map_dbl(IQR)
```





